\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{indentfirst} % Always indent first paragraphs
\usepackage{hyperref} % Allows using \href function

\begin{document}

\section*{Once Upon A Time In Stinking Springs}

***Abilene, Kansas, 1910. A man wearing a red poncho and a spanish quarter necklace rides in his trusty steed.***

???: Whoa! Easy, boy.

***It's a time of change, where the wild inches of the country smoothly surrender to the contemporary era. He hitches his horse and walks into the Bull Head's Saloon. A young boy is sitting with two men. He walks to the bartender.***

Ben: Don't I know you, sir?

Silas: Don't believe so. I haven't been here in many years. Name's Silas Graves.

Dwight: Silas Greaves? The bounty hunter?

Silas: Used to be.

Ben: What are you doing here in Abilene?

Silas: Just passing through. Got a little business to take care of.

Dwight: Well, sir, it would be an honor if you would allow me to buy you a beer.

Silas: Well, son, it would be my honor to drink it. ***Top tier one-liner.***

Molly: I'm Molly. Howdy.

Dwight: And I'm Dwight. That's Jack and Steve. Ben's behind the bar. I bet you got some great stories!

Silas: A couple.

Jack: Any of 'em true?

Molly: Jack, be nice.

Silas: A few.

Dwight: What about your shootout with Henry Plummer's gang... in Bannack, Montana? Is that where you started as a bounty hunter? That's what it says in this here dime novel.

Silas: Don't believe everything you read in dime novels, boy.

***The quintet gathers around to listen to his stories.***

Silas: First man I hunted was back when I was riding with Billy the Kid.

Dwight: You knew Billy the Kid?

Silas: Damn right. That scrawny son of a bitch had no fear. Wouldn't back down for nobody.

Dwight: I heard he collected the tin stars off any crooked lawmen who crossed him.

Ben: It was a war, boy, the Lincoln County war. And Billy promised his Regulators would take the life of every bastard who helped bushwhack John Tunstall.

Silas: The Kid had a big chip on his shoulder and hair trigger temper. That made him dangerous as hell.

\begin{quote}
    Stinking Springs, NM (New Mexico)

    December 23, 1880
\end{quote}

Silas: It was about 30 years ago. Billy was hiding out in an abandoned farm near Stinking Springs. I threw in with the Kid because the man I had sworn vengeance on was riding with his enemies. But before I tell you why I wanted that son of a bitch dead, let me tell you what happened that day: I was heading back to the hideout when suddenly I had this funny feeling.

Steve: Funny ha ha?

Silas: No, Steve, the other kind of funny.

***A dialogue enters here... Several dialogues of the game can be skipped if the player is fast enough.***

Silas: I knew those two morons would never let me through. I had no choice...

Ben: Was it Pat Garrett's posse?

Silas: Oh yeah. I heard the shots and I knew I had to move fast. Garrett and his army of deputies had surrounded the entire homestead. I decided to help Billy and the boys out a bit. So that's just what I did. As the Governor of New Mexico was paying for the Kid's apprehension, Garrett was able to hire every gun hand in Lincoln County.

***Silas sneaks into a gap in a barn towards the hideout area.***

Silas: Garrett's men were running around like a bunch of chickens with their heads cut off. Still, one of them reached the water tower. Not a bad idea. It would be a turkey shoot from up there. Luckily, these shooters Garrett hires weren't the sharpest tools in the shed.

***If Silas climbed the water tower***

Silas: The right position is very important. Personally, I prefer to be on top.

Molly: Oh you do, don't you?

Silas: Indeed, darling, but where was I? Oh, yeah. ***The weapon choice is also very important: Rifle deals the most damage. Quickshooter have the best fire rate. With the right skills unlocked, you can maximize the Six-shooter potential when double-wielding it and crouching. Ranger deals average damage, but has decent ironsight.***

***END OF ALTERNATE ROUTE***

Silas: A lot of them were saddle tramps of sodbusters or drunken drifters looking to make a few bucks. Then I heard a friendly voice, yelling at me from a window: "Back door! We'll cover you!". ***"Back of the door! We've got you covered!"*** Truth be told, things weren't much better behind the house. I cut their numbers in half, but that just made the ones that were left twice as mad. They made up for their lack of skill with a seemingly endless supply of ammo.

***Silas kills the enemies at the back door.***

Silas: It was a bit of a slog, but I finally fought my way around the back of the house. And like that, I was inside, none the worse for wear. I passed Dirty Dave, and upstairs I found Billy and Charlie Bowdre.

\textbf{***Crack shot, 21 killed by age 21, smart as a whip: Billy the Kid***}

Silas: Billy looked at me and said: "About time, amigo! Grab a gun and get to the window!"

Jack: Wait, so you were friends with Billy the Kid?

Silas: Yeah, sort of. Anyway, we were surrounded by dozens of deputized shooters who wanted to do us harm. I'm telling you, Garrett's men were dropping like flies but they just kept on coming. That's when Charlie got hit. "They're catching us in the crossfire!" - shouted Billy - "Get to the other side!"

***Silas clears the other side of the house.***

Silas: I don't know how many of those cracksuckers I personally put down, but it was pretty clear, even to Billy, that maybe discretion was the better part of valor.

Dwight: What's that mean?

Silas: It means that it was time to cut and run! "They got a gatling!" - Billy shouted - "Get the horses and bring them round back! I'll draw their attention!"

***The gatling is actually located far enough so it can hit Silas but he can't hit them. Silas can still take cover from it though. If the player stalls...***

Silas: I said it was time to cut and run!

***END OF ALTERNATE ROUTE***

Silas: He directed that order at me and I thought: "Why the hell do I have to do it?". Many would have fled in my place, but I had that false sense of invincibility that many young men have. Like Jack here.

Jack: What are you saying, old man?

Steve: Jack, he's just joshing with ya now.

Jack: Yeah, he better be.

Molly: Mr. Greaves, please continue.

Silas: Please, call me Silas, ma'am. Now where was I?

Dwight: You were heading for the barn.

Silas: Right. Making my way past a passel of fallen foes.

Dwight: Sounds like Garrett hired a whole Regiment of hired guns.

Silas: Yeah, and just when I thought I was done with 'em, more of these hapless bastards would pop up. But finally I had the stables within my reach... and that's when I met Sheriff Pat Garrett.

Dwight: I read that you went toe-to-toe with him, sir. That backstabbing bastard with that tacked on tin star. ***"Backstabbing bastard" sounds right since he killed Billy by shooting him in the back.***

\textbf{***Proud, handsome, ham-handed: Pat Garrett***}

Dwight: You challenged him to a showdown.

Silas: You read that in a dime novel?

Dwight: It said he showed no fear as he took your measure with eyes like a rattlesnake. And that you killed him... in a fair fight!

Steve: Is that what that penny dreadful said?

Silas: No, boy, that ain't what I meant when I said I MET Pat Garrett. So let me start again: I finally reached those damn stables... And stepped inside and... Bam! Last thing I heard was Garrett's voice: "That's not Billy..."

Dwight: And go on! How did it end?

Silas: End? Boy, that was just the beginning! ***Indeed it was.***

\section*{A Fistful Of Hot Lead}

Dwight: So what happened? Did Garrett arrest you?

Silas: Yeah, after I came to. Bastard had clocked me with his Colt.

Steve: And the Kid surrendered?

Silas: When he realized there was no getting out of there alive.

Jack: So they locked you up in Lincoln?

Silas: Indeed they did. Sentenced me to hang right along with the Kid.

\begin{quote}
    Lincoln Jail

    April 28, 1881 -Four months after the arrest of Silas Greaves
\end{quote}

Silas: It's important to know that I was only riding with Billy so I could find the bastard I was after. He was with John Kinney's gang and they were sworn enemies of Billy's Regulators.

Dwight: Why were you after him?

Silas: I owed that son of a fetch a bullet for what he had done to me and mine. Instead all I got for myself was a goddamn death sentence. Luckily it was right around then that I heard Billy make his move. He shot Jim Bell and a few other guards as he made his getaway. Later they wrote that some lady friend planted a pistol for him in the privy. What the papers didn't say is that Billy helped me escape too.

***A key falls in his cell.***

Silas: My first order of business was finding a firearm. Luckily, I located Deputy Bob Ollinger's mean-ass shotgun.

\textbf{***10 Gauge Whitney, loud as thunder, can cut a man clean in half: Bob Ollinger's Shotgun***}

Silas: I saw Billy through the window and he yelled I should take to the rooftops to make my escape. So I did. ***"Anyone saw Billy?"*** Hell yeah! That scattergun was like a double barreled howitzer! It could blow a man clear off his feet. You hardly had to aim the thing! ***Kinda sad it doesn't turn out that way on the outside... Shotguns aren't very effective.*** The Kid's escape raised a huge ruckus. Guards were everywhere looking for him. I had to jump from roof to roof like a damn alley cat. I followed the planks where I could, but... ***All the bad guys in the ground can actually be taken down... given Silas knows what he's doing.*** some of that wood was slippery as hell. The whole town was up in arms. And suddenly I was a fugitive.

Ben: So that bastard you were after, what did he do?

Silas: He did me and my family a grievous harm. But I knew if I was ever gonna find him, I would need to get my ever-loving ass out of there. I tried to be stealthy... and sneak my way past.

***Silas gets spotted...***

Silas: But Well if they weren't all waiting for me. Apparently, some of them thought I was Billy! See, me and the Kid shared a certain similarity in build and coloring. I was just glad I had Deputy Bob's mean-ass shotgun.

***Silas shoots his way through a shack.***

Silas: So much lead was whizzing by my head, it was like everyone in Lincoln wanted to put me in the ground. I knew I needed to find a horse. Though I never did have a great fondness for those four legged grass eaters. Smelly, sweaty, ungrateful beasts! We prize 'em too high if you ask me.

***At least, unlike Black Bart, his dislike for horses wasn't heavy enough to the point of him refusing to mount them.***

Jack: But where was the Kid while you were busy getting shot at?

Silas: Gone. And that's when it occurred to me why Billy set me free: So I could be a hapless decoy and draw attention while he snuck out of town. ***Shielders are not as tough as they seem.*** I knew if I made it out of there in one piece no one would put a price on my head.

Jack: Because everybody in Lincoln would be dead?

Silas: No, 'cause they all thought I was Billy, and all the blame would fall on him. Meanwhile, Deputy Bob Ollinger was organizing a posse to put me down. He was already a mean son of a bitch, but he was doubly pissed that I stole his mean-ass shotgun. Anyway, it was me or them and the only way forward led me straight to perdition. But the cards were dealt and I had no choice but to play 'em.

***Silas then fought his way down Lincoln County, heading for the stables... again.***

Silas: Finally, I found what I was looking for. The stables on the edge of town.

Jack: Guess Billy saved your ass, taking out Bob Ollinger the way he did.

***Indeed he did, with Bob's own mean-ass shotgun. But...***

Silas: Billy didn't kill Bob.

Jack: Sure, he did. He dispatched him right after he shot Deputy Bell.

Silas: No, sir. Because Bob came up right behind me angry as well that Billy had lit out. "Hello Bob", I said, "I think you better let me go". And he says: "I don't think so, boy. Not with my shotgun". So we stood there, in the middle of the street, eyeball to eyeball. He intended to kill me and I knew I had no choice but to defend myself.

***Silas never reached for his gun before his opponent.***

Silas: I killed him in a fair fight. Everybody saw I had no damn choice. Well, Lincoln got a mite depopulated that day. Pat Garrett gunned down Billy three months later, so his escape was all for naught anyway.

***Well, but if it wasn't for him, you wouldn't be talking to us today since he helped you escape.***

\section*{A Bullet For The Old Man}

Ben: So where'd you go after Lincoln?

Silas: Mexico. Until I realized nobody was looking for me. I ended up taking a job with the Rurales.

Ben: The Mexican Rurales?

Silas: I was hired to help 'em track down the Cowboys.

Dwight: The most vicious outlaw gang in Cochise County? Curly Bill Brocious, Johnny Ringo...

Jack: Led by Old Man Clanton himself.

Steve: They must have paid you a pretty penny to take them hombres on.

Silas: Not really, but truth be told, I had my own reasons for going after those boys...

\begin{quote}
    Guadalupe Canyon
    
    August 13, 1881 -A few months after the escape from Lincoln
\end{quote}

Ben: So was the bastard you were after now riding with the Cowboys?

Silas: Roscoe "Bob" Bryant was his name.

Ben: Oh.

Silas: But, no, this time it was a different bastard I was after. The aforementioned Mr. Ringo.

Silas: I came upon them robbing a stagecoach, which wasn't surprising being they were such murderous thieves and bastards. The bandits wore red scarves, so I knew they worked for the Old Man. I did my best to help those poor passengers.

***Silas deals with the robbers***

Silas: Moments later the attackers were dead and I checked the stagecoach to see how many passengers were still breathing: None. It was then I wondered if the rocks weren't hiding more bandits. Was that all of 'em? Or did I just hit the rearguard? I quickly got my answer: They attacked from on high, like Apaches often did. They'd appear in great number from above and rain down lead on their hapless enemy's heads. Making use of the high ground and whatever else they had. Yep, the Apaches always appeared out of nowhere and there never seemed to be an end to them.

Jack: Hold on, were you attacked by Apaches? What happened to the Cowboys?

Silas: Did I say there were Apaches? I said Clanton's Cowboys attacked me Apache STYLE.

***If you take a look back in the transcript, Silas said "They attacked from on high, LIKE Apaches often did". Cowboys appear now.***

Silas: I was in a pitched battle, but I was holding my own against an overwhelming enemy force. See, at the time, I was still pretty green and would often blunder into regrettable situations. But I just kept shooting at anything I could see up in those damn rocks.

***Silas deals with some of those Cowboys.***

Silas: I didn't see Ringo, but I knew he was with the Cowboys. He and Roscoe "Bob" had done me a dreadful wrong and I was determined to have my revenge. But to get to Ringo, I knew I'd have to fight my way past these other assholes first.

Silas: Unfortunately, I was running out of ammo. ***Ammo counters are reduced from 25 to 10 pistol rounds, 10 rifle cartridges and 10 shotgun shells on reserve.*** Another perfect example of my relative inexperience as a hunter of men. I immediately knew that a tactical retreat was called for as my vengeful fury was much less impressive without the bullets to back it up. Finally they managed to corner me. Trapped as I was, the odds of my survival seemed pretty slim. Luckily, serendipity was on my side as I suddenly spotted a way out of my predicament.

***Make sure to grab the Nugget of Truth on the way, but don't hold for too long.***

Silas: I ran ahead as if the devil himself was after me. Bullets were whizzing by my ears, but I wasn't about to roll over and die. I just kept running like there was no tomorrow. Because there wouldn't be if Clanton and his men caught up with me. As I was scurrying around those caves, I thought: "What was I thinking? Going up against a gang like this?". I just kept running, not knowing where the Heaven I was going. And that's when something miraculous happened. Like manna from Heaven!

***An Apache corpse falls.***

Silas: I found the desiccated remains of what looked like an Apache warrior. The old weapon next to him supplied me with some much needed ammunition. Bat Masterson once told me it's more important to be lucky than good and he would know. And imagine my surprise when I found a fistful of dynamite to go along with that ammo.

***With the right skill unlocked, time your dynamite split right so they fall close to each other. Triple dynamite, triple damage.***

Silas: That stroke of good fortune evened the odds and bolstered my confidence. It was time to turn the tables. Time for the prey to become the predator. Time for the hunted to become the hunter. Time-

Jack: Alright, Jesus, we get it. They were right where you wanted them.

Silas: That's right, Jack. I was done running. And the Old Man's boys were not expecting that. No, sir. I came at them like a wildcat! My fury knew no bounds. It was finally time for that Old Man to pay for his sins!

\textbf{***Cranky, cantankerous, mean as well: Old Man Clanton***}

Silas: I yelled out at the top of my lungs: "CLANTON! I'M COMING FOR YA!". A little stealth might have made more sense to be perfectly honest. Because that old fool had a Gatling Gun and enough bullets to last him 'til Kingdom Come. But I knew I could not let that deter me. Not if I was to find and kill Ringo. I needed to get that Old Man off that gun. Let me tell you, that was the longest uphill climb of my entire damn life. Well, one of the longest. There was that one time I was pursuing Frank James, Jesse James' brother.

Dwight: Jesse James?

Silas: Perhaps we can talk about that one later. Now where was I? Right. I had Old Man Clanton in my sights. Most everyone thought it was the rurales who had come up against him in Guadalupe Canyon, but it was just me.

***Silas finishes Old Man Clanton and his backup.***

Silas: Apparently, one of the Cowboys made it out of there alive. And told Ike and Billy Clanton that it wasn't a Mexican who took their father's life that day. ***It wasn't Silas either, but...*** They just assumed it was one of the Earps. And that little misunderstanding eventually led to that legendary gunfight at the OK Corral.

\section*{Gunfight At The Sawmill}

\begin{quote}
    Iron Springs, AZ (Arizona)
    March 24, 1882 -Seven months after Old Man Clanton's death
\end{quote}

Silas: A few weeks after that dust up at the O.K. Corral I was still after Johnny Ringo. I had tracked him and the Cowboys to their hideout at a sawmill and they were loaded for bear.

Ben: So what exactly did Johnny Ringo do to piss you off?

Silas: Well, him and that other bastard...

Dwight: Roscoe "Bob" Bryant?

Silas: Yep. They both deserved to die and I promise I'll tell you why. But first I need to tell you about the Cowboys' new boss, Curly Bill Brocius.

***"Earps coming!" "Get ready boys!"***

Silas: Curly Bill took charge of the Cowboys upon the Old Man's demise, and after that gunfight at the OK Corral, the Clantons wanted revenge. So they murdered Morgan Earp and grievously wounded his older brother Virgil. Wyatt and Doc went on what became known as the vendetta ride, hunting those outlaws down. So when I showed up, that's who they thought I was.

***Lifted logs fall.***

Silas: There were killers around every corner, all wearing red bandanas. That's how the Cowboys identified each other and I was beginning to wish I had one myself. But I wasn't about to let Ringo walk away unscathed and that's what drove me forward.

***Silas can shoot the rope of the logs lifted above the three gunslingers once they're in place.***

Dwight: They say that Ringo was infernally fast.

Ben: I hardly saw anyone faster, boy. Certainly not Wyatt Earp. That man was all hat and no cattle.

Silas: Earp wasn't much of a match for him, but Doc Holliday might have taken him. ***Indeed he did.***

Ben: That lunger should have kept his nose out of it. They never charged anyone for the murder of Morgan Earp.

Silas: But everybody knew that Curly shot him in the back. That was common knowledge.

Ben: Maybe so, but Ringo had nothing to do with it. He was just being loyal to a friend.

Silas: Is that what you call it? Being loyal? ***Silas says something about getting past some buzzsaws as big as a man here.***

Dwight: Excuse me, sir, I have a question.

Silas: What's that, Dwight?

Dwight: After Old Man Clanton died, why didn't his son take over the Cowboys?

Silas: Because Ike Clanton was dumber than a box of rocks and a yellow belly to boot. Now where was I?

Jack: Taking down the entire Cowboy gang single-handed.

Silas: Indeed I was, Jack. Though it wasn't easy as those boys had good cover.

***The shack to the left is enterable. And there's ammo in it.***

Silas: There were carts everywhere, piles of lumber and a God knows what else for people to hide behind. That really was one helluva sawmill. Quite an impressive operation.

Ben: And where was Curly Bill? Did you see him?

Silas: I'm about to get to that, Ben. Patience. I painting a picture here: There was this beautiful waterfall and a crystal clear stream that led to a verdant valley that was truly- ***Magnificent.***

Ben: Consider your picture painted. What happened next?

Silas: Well, finally the bastards that were still alive made a last stand.

***That "verdant valley" looks like the Ozarks. This game is divided into three areas: Borderlands, Wilderness and Train. The scripts define which locations of each area will be used for each level and how. Also, the lumber yard is surrounded by the sawmill route Silas went through.***

Silas: Curly Bill, Johnny Ringo and his compadres took off into the lumber yard and I followed after.

\textbf{***Takes a shot... before he takes a shot: Curly Bill***}

Ben: Are you saying they ran? Cowardice was not in Ringo nor Curly Bill's nature.

Silas: No sir. I never said they were running scared. They just wanted me out in the open.

***Curly: Time to dance with the devil!***

Silas: Brocius gave me no choice but to take his life. But Ringo was nowhere to be found.

Jack: I knew you didn't kill Ringo because he was found dead in a different location altogether.

Dwight: To this day his killer is still unknown.

Silas: Indeed. It took me a few months before I finally tracked his ass to West Turkey Creek Canyon.

\textbf{***Next in line to take over... and take a bullet: Johnny Ringo***}

***Ringo uses the same animation as Curly, but with a cigar instead of a bottle.***

\begin{quote}
    Turkey Creek Canyon
    
    July 13, 1882 -A few months after Curly Bill bought it
\end{quote}

Dwight: That's incredible, sir! I always thought that Doc Holliday was the one who killed him. ***But wasn't his killer unknown as of up to 1910?***

***Duels are not affected by game difficulty.***

Silas: Sorry I had to ruin the legend for you, boy, but the legend ain't always true. Doc Holliday had nothing to do with the death of Johnny Ringo.

***One down, two to go.***

\section*{The Magnificent One}

Silas: I was paid a healthy bounty for Ringo and Curly Bill and realized there was real money to be made. That's why I went after Henry Plummer.

Ben: Wasn't he the sheriff who augmented his income by shaking down miners and robbing gold shipments?

Silas: That's the one.

Steve: Oh yeah, I remember him. He ran that gang of thieving outlaws called The Innocents.

Dwight: So it's true that you went toe-to-toe with him?

Silas: Indeed I did, son. Indeed I did.

\begin{quote}
    Near Bannack
    
    Some time after Johnny Ringo's death
\end{quote}

Silas: I knew I needed resources if I was gonna track down Roscoe "Bob" Bryant. And hunting Plummer looked like a good way to get rich quick. As the local vigilantes exposed him as the leader of the bandits, and put a generous price on his head. Plummer rallied his gang to plunder one last gold mine before making their escape and that's where I thought I'd find him.

***"It makes me nervous staying so close to all these goddamn barrels of gunpowder!" "Why would you be nervous? No one has the cojones to come after us! Plums, y'know light up a cigar, we're fine!" "And besides, George is up there on the rocks with that rifle of his. Nothing gets past him!"***

Silas: As my late father pointed out to me more than once: "God made men, but Samuel Colt made 'em equal". ***Amen.*** I knew that dynamite wasn't mine, so I decided the polite thing would be to return it.

***Concentration is key. Don't hesitate to spend it. Especially after getting the right skills.***

Silas: It was the biggest gold rush since Sutter's Mill in '48. Unfortunately, prospectors weren't the only ones drawn to those riches. There were thieves and killers robbing travelers and hijacking gold shipments. Like those who ran with Plummer. Some were just regular folks I knew from town, drawn by greed and easy pickings. Charlie Crowe, the blacksmith. James, who worked in the stable. Sam and Jeremiah Barber, the butcher's sons. Ordinary citizens who lived a double life.

***The late parts of that dialogue are skipped if Silas passes through that section too fast.***

Silas: Course the rest were veterans of the Civil War. Stone cold killers trained on the bloody fields of Shiloh and Antietam. Plummer had a lot of man on his payroll. A well of a lot. That son of a bitch pretended to protect the public with one hand while stealing them blind with the other. He set up a defensive perimeter which I had no idea how to breach. Dangerous, desperate individuals. I was outnumbered and in way over my head, but I was too damn stubborn and stupid to realize it. They must have thought I was touched. Or had some kind of death wish. Seeing as there were barrels of gunpowder everywhere. I thought I was some kind of hero.

***Silas gets past the barns with the explosives.***

Silas: I finally made it past and headed on to meet my destiny. But first I had something I needed to figure it out.

***Silas approaches the mine entrance.***

Silas: I had a few ideas on how to get into that mine, but once I made my decision, I knew there was no turning back. So my first thought was to enter the nearest mine portal. I saw an entrance. Made sense.

***Difficulty for Recollections Mode cannot be changed. They always play at Normal.***

Silas: It was the quickest in, but that also made it more dangerous. As there'd undoubtedly be enemy pickets along the way. Besides, once you enter a mine like that, it's easy to get all turned around. And that confusing maze of corridors wouldn't even be the worst of it. Some of those shafts can be deep as Well. A single stumble or misstep can easily end in a deadly plunge to oblivion.

***"I do not deserve to die like this!"***

Silas: Quick reflexes often make up for a lack of common sense. Luckily, I was never one to be easily bushwhacked. I would just need to be careful not to blow myself to Kingdom Come. With all the gunpowder and dynamite everywhere, a body has to know what he's shooting at.

***It's safe to toss a dynamite before entering the broken staircase and clear the first round of powder, but the second one will always result in kill if one of them gets hit no matter what -except for the following scripted sequence. Also avoid using the rifle in situations like these, the high-power caliber of this weapon can hit the powder by crossing straight through the bad guy. If Silas "died" from the second powder stack...***

Silas: All it takes is one tiny spark and boom!

***END OF ALTERNATE ROUTE***

Silas: One wrong bullet could have turned that mine into a dad-blasted tomb! I freely admit that my plan of attack was not just moronic, but clearly insane. ***A mine cart falls into Silas. It's the only moment in the game "YOU ARE DEAD" appears without sending the player back to the last checkpoint.*** It's a good thing that I abandoned that ridiculous plan before I even tried it.

***Silas is “returned” to the mine entrance.***

Silas: Instead, I spotted a ladder. A way into the mine from the opposite side. It was the long way around, but that approach seemed more sensible at the time. Of course, being I had a problem with heights, that scaffolding scared the bejesus out of me. Climbing down that ladder required some caution. 'Cause even though I had a younger man's reflexes, no man can dodge a damn bullet while climbing down a rickety ladder. I needed to make a leap of faith. Which ain't easy when you're suspended between Heaven and Hell.

***Silas jumps to the leap, only to fall in the leap below.***

Silas: I was determined not to give up however. As sheriff Plummer seemed quite the despicable character. When the vigilantes discovered what the sheriff was up to, people were outraged. That ten thousand they put on his head would go a long way to helping me find old Bob. And I had made it my mission to settle that score come hell or high water. But first, I would have to make a choice: Take the elevator or climb a ladder.

***If Silas took the elevator...***

Silas: I picked the more convenient and more dangerous route. ***Especially with two bad guys waiting at the top.***

***If Silas climbed the ladder...***

Silas: I wanted to use the element of surprise. Plus I figured I could use the exercise. I was warmed up already, so what the hell.

***END OF ALTERNATE ROUTE***

Silas: Plummer was a mad dog killer and the people of Nevada City deserved better.

Ben: Nevada City? But I thought Plummer met his maker in Bannack, Montana.

Silas: Right, well, he was the sheriff in both places at one time or another, but that's neither here nor there. The point was taking him down would save a lot of lives. Including my own.

\textbf{***Lawman, outlaw, scalawag: Henry Plummer***}

***Henry: Catch this, you son of a bitch! Well, this day is just getting worse and worse for you, ain't it!***

Silas: Henry Plummer was clearly unhinged and I could see right away this was gonna take some doing.

***Silas gets halfway done with Henry***

Henry: ***Guess you had enough!*** Goddamn! I need some help here! Come on boys! Take this cocksucker out!

***Silas dispatches the reinforcements and Henry returns.***

Silas: So that's how Henry Plummer died. Him and his crew were worth their weight in gold. ***Indeed they were.*** And now I was officially a bounty hunter.

***If it seems too easy after all, don't be afraid of increasing difficulty. This ain't your unbalanced first-person shooter: Despite Silas having less health on Hard difficulty and minimum health with HUD disabled on True West difficulty, plenty of cover and precise shots always get the job done.***

\section*{Be Quick Or Be Dead}

Steve: So did you finally go after that Bob feller? ***Feller=Fellow***

Silas: Well I heard word he was in Kansas with John Wesley Hardin, so that's where I went.

Ben: Where in Kansas?

Silas: Abilene. Why do you ask, Ben?

Ben: No reason.

Dwight: Was Hardin as fast as Ringo?

Silas: Ringo was fast, but John Wesley was as fast as the devil himself. Well, he killed his first man at fifteen. ***Believe it or not, because he couldn't stand the man was snoring.*** From that day forward he had a price on his head and wouldn't back down for nobody. ***Just like William Henry McCarty a.k.a. William H. Bonney, Kid Antrim or simply Billy the Kid.*** Not even Wild Bill Hickok himself. ***Not to mistake it with Wild Bill Hiccup.***
 \begin{quote}
    Abilene, KS (Kansas)
    
    Nearly 30 years ago ***After Henry Plummer's death***
 \end{quote}

***Some uses of the Sense of Death throughout the stories are scripted.***

Silas: I dodged death many a time and that night in Abilene was no different. I was there with the intention of finding that bastard Bob and collecting the bounty on John Wesley.

Ben: Oh, I thought the Texas Rangers got Hardin? ***But they did, as Silas is about to tell us.***

Silas: Yeah, that's what they want you to believe. It was colder than a witch's tit in a brass bra that night as I fought my way past his loyal compadres... To the very same saloon we're sitting in today. Look around and imagine this place painted in blood. Hardin was waiting for me and- Wait, I'm jumping the gun here. Let me back up and give you some background on this sumbitch. He deserves that much. Don't you think so, Ben?

\begin{quote}
    Earlier that night, in the vicinity of Abilene
\end{quote}

Silas: John Wesley Hardin was a killer. By the end he confessed to taking the lives of 42 men. He was a bonafide folk hero by then and had amassed a gang of armed miscreants and other assorted thugs.

***In both moments of the level, before entering the Bull's Head Saloon, it's possible to explore a good chunk of the level, which is a reskinned Lincoln County -and Coffeyville, and maybe Parachute, it's the same town anyway. You can even see Stinking Springs at a high spot, but you obviously can't access it because they tossed a massive rock on the way in the hopes players wouldn't notice the reskin and think of it as a fresh new level. The Lincoln County jail can also be seen by heading to the left side of the town right after entering it.***

Silas: He and his men set up camp outside of town and I was hoping Bob was among them.

***"Shit, it's cold out here! Freezing my tiblets on. It ain't right we got to stay out here keeping watch like this!" "Ain't nobody stupid enough to go after Hardin anyway..."***

Silas: Better three hours early than a minute too late. ***"Damn it! Shoot that son of a bitch!"***

***Silas can head to Abilene through the upper side of the cliff and skip a good chunk of firefight.***

Silas: They didn't ask why I was there. They knew. As most of them were wanted as well. I figured Hardin was here somewhere, but to get to him I'd have to get past his gun hands. I had to spill a lot of blood to find out Hardin wasn't in that camp. He was carousing in town with his closest friends. Hardin's boys apparently didn't want me to reach the Bull's Head. Some were high-tailing into town to inform their jefe of my unwelcome presence. And I steeled myself for the fight ahead. For as good as I was, deep down I wondered if John Wesley wasn't just a little bit better.

***Silas arrives in Abilene.***

Silas: Before I could test my mettle against Hardin, however, I would first need to dispatch his cadre of hired killers. Most of these degenerates were beyond redemption, but John Wesley might have been a different story. I didn't learn until later that that night was, in fact, his birthday celebration.

***Then Silas proceeds to clear the Bull's Head's surroundings.***

Silas: I think I already mentioned that I found Hardin in this very saloon. Suffice it to say, nobody there was happy to see me. In fact, I felt a certain... hostility.

***Silas wipes the bad guys inside the Bull's Head. Due to entertainment purposes, the painting of a bull with his huge dick out is absent.***

Silas: I was disappointed that neither Bob nor John Wesley were among the dead. But that was short lived as a moment later I was facing down the fastest gun in the West.

\textbf{***First kill at 15: Killed a man for snoring, and forty more for breathing: John Wesley Hardin***}

Silas: I felt a bolt of adrenaline. Or maybe that was fear. He was well known for his tricks and I knew I'd need my own if I was ever to defeat him.

***Just make sure to charge your focus and speed. Since Hardin was a tough nail, Silas couldn't hit him. HOWEVER, shall the player be unlucky enough...***

Silas: No, wait, he didn't shoot me. I can grant you that.

***There are other two lines he spits out in this situation, but I won't mention them because it's rare given the player is used to the duels.***

***END OF ALTERNATE ROUTE***

Silas: That man was faster than greased lightning. But being inebriated as he was he didn't count his shots. And now he was at my mercy.

Dwight: So he didn't die?

Silas: No, I sent him to prison. But years later, after he was free, some restless avenger took his life. Shot him in the back in a saloon just like this one. Anybody up for another beer? Ben?

\section*{Dances With Renegades}

Silas: Thank you, darlin'. Yeah, some say revenge is a dish best served cold.

Dwight: So what ever happened to that Bob guy you were after?

Ben: Personally, I'd like to hear some of your other adventures. Like, uh, I don't know... You ever go toe-to-toe with the red man? ***Ben, let Dwight hear the story.***

Silas: Yes, I did, Ben. I remember once I was after this renegade Apache, Grey Wolf. Strangely enough, revenge was also his primary motivation.

***Silas may remind you of John Marston, but he's actually mostly based on Frank Eaton.***

\begin{quote}
    A long time ago
    
    On a mountain far, far away... ***Presumably the Ozarks, as we'll see later.***
\end{quote}

Silas: A bounty was put on Grey Wolf's head and that is how I came to hunt him in the mountains. Mountains so high they tickled the nether regions of Heaven. Grey Wolf was a Chiricahua Apache medicine man who had led a war party in revenge for a massacre against his people. The U.S. Army had attacked his tribe during his daughter's sacred sunrise ceremony and the slaughter was unspeakable. I understood his anger, as there's nothing more traumatic than seeing those you love die in a cruel and painful death.

***Silas spots a wolf on an elevated rock.***

Silas: Right from the beginning I couldn't shake the feeling that Grey Wolf was watching my every move. He led a band of young Apache warriors who wanted retribution and were more than willing to die for him. They saw me before I saw them.

***With the right skill unlocked, you can exact your revenge on who made Silas spend his Sense of Death. But don't push your luck...***

Silas: And it crossed my mind that maybe this wasn't such a good idea. But now that the shooting had started, there was no backing down.

***Silas shakes hands with some melee brawlers.***

Silas: It was rugged country, the winter home of the Chiricahuas, and that's why they had retreated there. ***"Chiricahua" is pronounced "Chiracaua".*** I admit to having some regrets about going after them the way I did. But then again... I got a lot of those.

Dwight: Did you find Grey Wolf?

Silas: Not at that moment, but I did find the entrance to their hideout.

***Silas should be able to see the entrance opening.***

Silas: A deep crevice that led to a deeper cave.

Molly: Don't tell me you went in there?

Silas: Yeah but is not out of bravery so much as pure angry cussedness. See, back then, I had a stubborn streak a mile wide and I wasn't about to back down.

Dwight: So it was, like, pitch black in there?

Silas: Actually, it was pretty well lit as they had torches on the walls.

Ben: So how big was this cave?

Silas: Big as well, Ben. The Chiricahua had hid out there during the Indian Wars. They thought it was haunted with the ghosts of those murdered by the horse soldiers.

Dwight: The cave was haunted with dead Indian ghosts?

***Just a friendly reminder that a failed Quick-Time Event will result in a use of Sense of Death... if it's 
charged.***

Silas: To be honest, I was more concerned with the live ones than the dead ones.

Jack: How come you know so much about injuns?

Silas: A few years back, I was married to two Mescalero women.

Molly: At the same time?

Silas: Yeah, they were sisters. Polygyny is traditional among the Mescalero.

Dwight: So what happened?

***I don't think anyone listening to the stories was interested in the details.***

Silas: Had to get out of there. Those girls never shut up. Both of 'em nagging at me all the time. Drove me half crazy. Haven't seen 'em since.

Dwight: No, I mean what happened with Grey Wolf?

Silas: Oh! Well, I pursued him into the cave of death. I came upon this flooded grotto and that's when I saw him. He came to me unarmed and unafraid. His voice echoed in the shadows. And I sensed he meant me no harm.

Grey Wolf: You carry great darkness in your heart and if you do not release it, it will claim your soul.

***Maybe revenge is a fool's game after all...***

Silas: The sound of his voice put some ancient Indian spell on me.

***Cuts to "Without Forgiveness", just before the question.***

Silas: As his story unfolded in my mind.

Grey Wolf: You will come to this place again and kill many more men and the darkness will grow until it consumes everything that you are. The soul would have no rainbow if the eye had no tears.

Silas: He said I was a great warrior, a coyote-man. Unequaled by any other paleface warrior. Or something like that.

Grey Wolf: The snakes will bite shadows of your past until the venom poisons your heart and an echo of the song of the dead summons the spirits deep from within the mountains.

Silas: I didn't quite get what he was saying but there was definitely snakes.

***Cuts back to the grotto.***

Silas: And indeed. His warriors surrounded me and attacked me like hungry wolverines. They couldn't stop me though and Grey Wolf wasn't in the mood for idle talk.

***Silas deals with the first Chiricahua ambush.***

Silas: I swear I couldn't see any way out of this trap, but suddenly one just appeared, kinda like a miracle.

***A staircase to the higher ground of the grotto rises from the middle of the water.***

Silas: Finally, I found myself back outside perched on the edge of a precipice overlooking a thundering white water river. To get where I was going required several leaps of faith, but no way in well I was turning back. I chased after him, determined to make him explain the meaning of all that mumbo jumbo.

***Silas said: "He came to me unarmed and unafraid. His voice echoed in the shadows. And I sensed he meant me no harm." So it's obvious Grey Wolf wasn't holding a firearm.***

Jack: Mumbo jumbo is right. Are you making this all up as you go?

Silas: A few details may be fuzzy, brother, but I am relating exactly what happened to me. There were dozens of Apache warriors aiming at me from on high.

Jack: Dozens?

Silas: Well maybe not dozens, but there was a lot of 'em.

Molly: At least three or four?

Silas: Well, more than that, little lady.

***If Silas is fast enough, he'll spot Grey Wolf running before disappearing into the cliffs.***

Silas: I had a steep climb up creek ahead of me and scrambled up those rocks like a mountain goat. I was determined to locate Grey Wolf and find out exactly what the hell he was trying to tell me. And wouldn't you know it: That crafty son of a bitch led me right into a trap.

Dwight: What kind of trap?

Silas: Well son, there had to be at least a hundred Apache surrounding me.

Jack: A hundred?

Silas: God be my witness!

Jack: Ho-ho, come on, who're you kidding?

Dwight: Hey! I-I believe you! Come on, tell us how it ended!

***Dwight was the only one interested in the stories anyway...***

Silas: All right, but I'm not gonna drag this out. Where were we?

Jack: You were surrounded by a hundred Apache warriors.

Silas: Well I didn't take the time to count 'em exactly, but there were a lot of 'em.

***Some melee brawlers will ambush Silas before more attackers "from on high" show up.***

Silas: And in the end a path appeared before me that I had not seen before. ***Had not?*** I followed it as I desperately needed to find out what Grey Wolf was trying to tell me. ***He was so busy with the attackers he forgot which one of them had the bounty on.*** But it was like that sumbitch disappeared into thin air. Never did find him. And never did collect my goddamn bounty. ***The bounty is a lie.***

\section*{They Call Me Bounty Hunter}

Silas: Thank you, darlin'. It's interesting how the truth can sometimes seem, uh, a might... malleable depending on your point of view.

Jack: Like how those dime novels make you out to be something you're not? ***Says the man who doesn't trust him...***

Molly: Jack, don't be starting trouble.

Silas: No, he's right. They... do tend to exaggerate.

Dwight: Did they exaggerate your part in taking down the Daltons? ***Indeed they did, boy.***

Ben: Well I was there in the flesh, boy, so I saw what happened first hand.

***Death Finds The Dalton Brothers: The True Story Of Coffeyville***

Ben: Those Daltons were lawmen once before they all went bad, robbing banks and trains clear across the territory. Until Coffeyville, of course. I was one of the citizens who took up arms that day.

Silas: Fighting on the side of right? ***Silas, at this rate, is sure this bartender, listening to these same stories as we are, is the very same man he spent the last 40 years of his life hunting down.***

Ben: I did my best sir. We all did.

\begin{quote}
    Coffeyville, KS
    
    October 5, 1892 -9:10 AM
\end{quote}

Ben: It was early morning. One of my friends was the local gunsmith and he handed out firearms to anybody who'd take one. You see, the Daltons got it in their heads to rob two banks at the same. Two banks on the same damn street!

***Two observations:

1) Only the approach to one bank is followed due to "storytelling restrictions" and the fact Coffeyville uses, in fact, only the upper side of Lincoln County/Abilene/Parachute level. Just so you can have an idea, the saloon in this level has the Bull's Head assets from the Abilene level. Also, the "Federal Bank" assets are absent in both previous levels. It's a good thing this game is decent, otherwise this would be a Bad Quality.

2) What kind of gang, back then, would be idiot enough to rob two banks... at the same time... at the very same town they already had a bad reputation on? Even the Van Der Lindes weren't this idiots.***

Ben: Story was Bob Dalton's girl was always riding him about how he had no ambition. "Oh you're nobody next to Jesse James", she'd say. Finally, the bastard took his brothers to Coffeyville just to shut her up.

***Molly says "Always the woman, isn't it?" at this part, but for some reason, walkthroughs around the internet seem to skip this part...***

Ben: Well the locals recognized the Daltons right off. ***Pacific Southwest Railway Bank Inc., except the Daltons weren't no longer there by then. Looks like Silas ain't the only one making stuff up...*** Before they could get away, half the town took up arms to defend their property. ***One of them actually escaped... But he didn't go far.*** Their first mistake was pulling a job in their own damn hometown! The brothers paid dearly for their stupidity, but everybody knows... they had it coming-

Dwight: There's more to it than that. I read all about that day, so I know for fact it went down very differently.

***Seriously that Dwight is bringing up these penny dreadfuls again?***

\begin{quote}
    Coffeyville, KS
    
    October 5, 1892 -11:55 AM
\end{quote}

Dwight: First of all, it was high noon. A posse of U.S. Deputy Marshals were on the rooftop across the street. ***"Get ready, boys! They're gonna make a move!"*** The lawmen had been tracking the Daltons for months and now they had 'em dead to rights. Among them was a bounty hunter feared by many a lawbreaker. The Marshals tried to get the Daltons to surrender... ***"Don't give up eventually. We just gotta wait the sons of bitches out."*** But this bounty hunter knew that the brothers were far too proud to ever lay down their guns. So he went in there alone to confront those criminals.

***A ladder the player didn't spot before appears to the left side.***

Dwight: One of the Marshals shouted "Where are you going, are you crazy?!" ***"Hey, where you think you going?"*** He saw a way to get around to the back of the bank. ***That no one noticed. Sounds just right.*** Then he figured out how to hit the Daltons from a direction they weren't expecting. A moment later, he was climbing up a steep ladder, laughing at danger as he did. ***At least they got his fear of heights right.*** It was brave men like him who risked their lives to tame this wild country. Heroic men like him who did what other men couldn't or wouldn't to make this country free. ***"Is that Silas Greaves?" "Son of a bitch!"*** Like Jim Bowie and Davy Crockett who died defending the Alamo. ***"You can't hide from me!"***

***"Over there!" "That's Silas Greaves!" "What the hell!"***

Dwight: Blam, blam! He came away victorious, taking down those thieving Daltons. His name was Silas Greaves. And when the dust finally settled, he was the last man standing.

Silas: Sorry, kid, but that just wasn't the way it happened.

\begin{quote}
    Coffeyville, KS
    
    October 5, 1892 -6:50 PM
\end{quote}

Silas: It was early evening, not high noon. The Daltons blew up the safe and were all set to hightail it out of there. I was late to the party and Coffeyville was already up in arms. Those pathetic deputies surrounding the bank were dropping like flies.

***FEDERAL BANK*** \textbf{***(Bob) The Leader, (Emmett) The Lover, (Grat) The Loser: The Dalton Brothers***}

Silas: I'd been tracking those jokers for months waiting for them to do something reckless. And finally they did: Those stupid bastards decided to rob two banks at the same time in the same town where everybody knew 'em. But they still had friends in Coffeyville. ***"Keep shooting! I don't mind." -Shielder*** And those friends came at me like a pack of wild dogs. Tooth and nail! They were coming at me from all directions. I caught sight of the Daltons running with the money and I didn't want to lose 'em. The problem was, they knew the town better than I did. And to top it all, I found myself in the middle of another shootout entirely.

Dwight: Did the Daltons hole up in somebody's house?

Silas: No, it was the, uh, Smiths, I believe. They were cousins of the Daltons. And they were shooting at the Browns, who were shooting at the Daltons. Which wasn't any surprise as those two families have been feuding forever. ***The shootout between the Smiths and the Browns had nothing to do with the Daltons' robbery, though.*** And since the Jones' are related to the Browns, they shot at the Smiths, pissing off the Heimhoffers, whose daughter recently married a Smith. ***As I said, nothing to do with the robbery.*** Well, bullets were flying every which way as all the old feuds in Kansas caught fire all at once. There was a hell of a lot of pissed off people in Coffeyville that day. But that's just the way life is sometimes: Shit happens.

***Notice the shack Silas walks through at this part is the very same shack model used in "Once Upon A Time In Stinking Springs", where Billy, Charlie, Dirty Dave and Silas held up against the Garrett's Posse.***

Silas: The Dalton boys knew I would never give up. Those Daltons weren't the sharpest knives in the drawer, but they always stood together. They set a trap to slow me down and allow at least two of them to escape. ***Uncommonly this last line won't appear in the subtitles. Also, there are a lot of punctuation typos and missing words in the subtitles. Was the game development rushed?***

Silas: It was Emmett, the youngest. And he decided to stand his ground and face me down.

Emmett: I ain't afraid of you, Silas Greaves! This is where it ends for you!

Silas: He was determined to protect his brothers and I understood how he felt. But taking me on all by his lonesome wasn't exactly a recipe for a long life.

***Emmett Dalton is resistant to concentration. He should take at least 15 shots to go down.***

Ben: But Emmett Dalton survived the robbery in Coffeyville. He's the only Dalton who did.

Dwight: They say he was shot twenty-three times.

Silas: Well Dwight, who do you think put all those damn holes in him? But I have to admit: That boy had grit.

\section*{Bounty Hunter Is Still My Name}

\begin{quote}
    Somewhere in Missouri
    
    Fall 1892 -Some time after the foiled bank robbery
\end{quote}

***"We'll get these suckers!"***

Silas: It took me a couple of days to track the Daltons down.

***"They can't get away with this!"***

Silas: And, in that time, a whole posse of local vigilantes offered to lend a hand.

***"We'll track 'em to the ends of the earth!"***

Silas: They seemed as determined as me to find those outlaws. But as we headed into those swamps, it was like I had my own private army. ***Something smells fishy about these vigilantes... They lost sight of Silas pretty quickly to my taste.*** There was no way those boys would get away this time.

Ben: It was early fall, right? Beautiful time of year. At least you had the weather on your side.

Silas: Not by my recollection. It was damp and foggy as well. ***Fog smoothly covers the swamps.*** It was tough to stay on a true course, so we kept an eye out for landmarks. ***But the level orientation is very linear, so it's very hard to get lost.*** It was Autumn, the maple trees were in full color. Red as blood. ***A pair of orange maple trees grow.*** The rains that year were torrential, so the whole area was flooded.

***"Fog and swamps hinder orientation. The waypoint indicator is disabled for this mission". But, as mentioned, it's very hard to get lost thanks to the linear level orientation. Also, bad guys start appearing at this part.***

Silas: The vigilantes had spread out wide and pretty soon I couldn't see anybody. Except for some sons of bitches ahead of me wanting to do me harm, so I had to face 'em alone. I wondered why my compatriots didn't come running when they heard the shots.

Jack: So did you find the Daltons?

Silas: Not yet. But I did have the questionable pleasure of meeting a few of their friends.

***The Saw-Off Rifle is as effective as the Regular Rifle, but it's the player's choice to take their chances.***

Silas: The boys had established quite a reputation by that time so they attracted all manner of riffraff to their cause.

***Watch out for dynamiters: Silas can airburst their dynamite. He can also take 'em out by shooting their dynamite bandoliers.***

Silas: Point being I was under serious attack and my reinforcements was nowhere to be seen.

***Shotgunners are weak to rifle headshots.***

Silas: But luckily, a barn materialized as if right before my eyes. I scrambled up top to get a better view. But just ended up falling inside.

Steve: So how did you g-get out?

Silas: The barn doors was open. ***Actually, the barn doors open after this line.*** About right then I saw some suspicious characters running for the bushes. Of course I followed them, but that goddamn swamp was like a goddamn maze and pretty soon I had no goddamn idea where I was. ***BO-RING.*** ***Steve snores.*** Steve? ***Steve snores again.*** So I just started walking and pretty soon e- ***Steve keeps snoring.*** Steve? Steve!

Steve: E-uh? Oh, no, no, I'm listening...

Silas: Indians surrounded me from all sides. ***You can take out a couple of them before the next line but it's not much use.***

Steve: ***Still sleepy*** Injuns?

Jack: There were Indians?

Silas: No... I just wanted to make sure Steve was paying attention. Now where was I?

Dwight: You were following the Daltons, through a swamp.

Silas: That's right. See Steve, Dwight's paying attention.

Steve: No, I-I'm listening. I-I-I was just, uh, resting my eyes. ***Don't worry, Steve, this episode is about to get more interesting soon...***

Silas: So, w-where was I? ***Even Silas has no idea what he's telling anymore.***

Dwight: The Daltons.

Silas: Right... See, there's a reason so many outlaw gangs made up of brothers: Being a brother is a very sacred thing, it's a bond like no other. ***That explains why Silas lost idea, but wait until you hear the reason why he became a bounty hunter... and yes, somehow it has something to do with family and brotherhood.***

Jack: So did you ever find the damn Daltons?

Silas: Not yet, but I did find a few of their cousins. You Kansans breed like rabbits: More Smiths or Heimhoffers or who knows what. But well, what's more important than family? I bet Ben knows what I'm talking about.

***Dynamite against shielders is very effective.***

Silas: I knew those Dalton boys were out there somewhere, standing together against anyone who would threaten them. And that's when I saw it: a goddamn steamboat.

Steve: A steamboat? In a swamp? ***Told ya, Steve.***

Silas: Yeah Steve, but this wasn't much more than a wreck, really.

Jack: But how'd a damn steamboat end up in the swamps?

Ben: Guess it floated off during the flood of '89. ***Wrecked steamboats were very common back then. They weren't reliable.***

Steve: Now was it a stern-wheeler or, or a side-wheeler? ***By the look of it, a stern-wheeler. But...***

Silas: Well, wh- Does that really make a difference, Steve? It was a steamboat. With a goddamn army on board!

***Cuts back to gameplay, with Silas relocated to the left side of the steamwreck.***

Silas: It was then that a fusillade of bullets came raining down from on high, and those vigilantes who had accompanied me weren't anywhere to be found ***He's starting to sound like those dime novels...*** But among those men that were shooting at me, I thought I saw some familiar faces. Somewhere up there the Daltons were waiting on me.

Ben: Sounds like you don't give up too easy. ***Sounds like?***

Silas: That's the kind of man I am, Ben: I set out to do something, I do it. Surrender just ain't in my nature. Plus I'm stubborn as hell. ***You already said that, dumbass.***

***Silas reaches the top of the steamboat.***

Silas: Right about then, much to my relief, the vigilantes finally arrived! Their leader motioned at a cabin in the middle of the top deck, pointing me directly at the Daltons. I finally had them, after months of dogged pursuit. ***Why is he talking about them as though he was talking about the Wild Bunch?*** But it turned out they had me. ***I knew there was something fishy about them!***

***"Take 'im out! I'm sending you to hell!" Indeed he did: The steamboat was caught on fire.***

Silas: The Daltons had played me like a fiddle. Apparently, the vigilantes were on their damn payroll! They didn't want to just shoot me: They wanted to burn me alive. But finding my way out of the burning labyrinth proved to be quite a challenge-

Jack: ***While Silas is still talking...*** It was a Riverboat, right? I mean, it's not like it was a goddamn ocean liner. ***Yeah, maybe the Dalton's saga after Coffeyville was actually that boring.***

Molly: ***Silas: Yeah, but I was in the-*** Did you hear about that ship that's gonna launch next year, largest one in the world?

Steve: ***Silas: Umm, well-*** You're talking about the Titanic? If you ask me, it's too blessed big. I don't think it'll even float.

Jack: ***Silas: So anyway-*** Don't be stupid, Steve. They know what they're doing: They say the Titanic is unsinkable! ***If only he knew...***

Silas: Oh Lord...

Dwight: ***He's paying attention, remember?*** But getting back to that steamboat, how'd you get off it Mr. Greaves? ***Call him Silas, please.***

Silas: I took in a lot of smoke that day, so I admit my recollection might be a bit hazy. ***Right...*** But somehow, I managed to finally... disembark. It was time to settle this once and for all. ***At True West difficulty, it's actually simple to orient the gatling shots despite the absence of the crosshairs.*** Bob and Grat weren't about to come at me one at a time. They were in this together.

***Aim for Grat (the Dalton behind) first.***

Silas: They got it wrong. A sad end for those two. If they only known that Emmett was still alive, despite his wounds. Paroled fourteen years later, he moved to California, sold real estate and lived off the legend of that fateful day. And the tragic death... of his two brothers.

\section*{Not So Great Train Robbery}

Silas: My own brothers died tragically as well, truth be told. ***Juarez 1868*** It was 1868 and me and my older brothers were pulling in a tidy profit running cattle into Juarez, Mexico. One night, after my brothers had retired for the evening, I found a little poker game in a cantina with a couple of cowboys. And I just couldn't lose. I even won an old Spanish coin that had to be a hundred years old. Well, I was mighty pleased with myself the next morning as my brothers and I rode for Texas. But, before we crossed the border, those cowboys caught up with us. It was Johnny Ringo, Roscoe "Bob" Bryant and another asshole named Jim. ***Reed. And indeed he was a big fat asshole, as we'll hear.*** They wanted their money back and everything else we had. ***One who just can't lose at poker is assumed they're cheating.*** Including our lives as those boys didn't want us coming for 'em later. ***Since they weren't into outlaw life, the Greaves brothers ended up becoming easy prey for them.*** Bob put that old Spanish coin in my mouth and said: "I won't have it said that I left you with nothing, boy". ***Ben probably was like "This can't be that kid... he looked so different back then."*** Well, those horses bolted and there we hung as those bastards rode away. The branch finally snapped under the weight of the three of us. But being my older brothers were bigger and heavier, they were already dead. And right then I swore to myself that I would avenge them. Ringo you know about, but Bob eluded me until I heard he was riding with the Wild Bunch.

\begin{quote}
    Wilcox, WY (Wyoming)
    
    June 2, 1899 -Nearly seven years after the Dalton's Demise
\end{quote}

Silas: I'd been on their trail for months ***Subtitles will write "their for trail months" instead.***, ever since they left their hideout in the Big Horn Mountains. Led by Butch Cassidy, they were a loose association of outlaws who robbed banks and trains from Colorado to Montana. Among them was the Sundance Kid and that murderous hombre I was tracking, Roscoe "Bob" Bryant.

Dwight: You were part of that giant Pinkerton posse after the Wild Bunch?

Silas: No, boy. A circus like that would have slowed me down. Besides, I wanted Bryant all to myself. I heard about a large shipment of gold being transported to Wilcox, Wyoming on the Overland Flyer. I figured the Wild Bunch would likely hit such a treasure and, by Lord, I figured right. They blew the bridge with the intention of forcing the train to stop. ***But they were stupid enough to blow the bridge with the train ON it instead of before it.*** Well I assumed the Wild Bunch was likely in the still intact part of the train high above. I was determined to make that sumbitch Bob pay for what he did to my brothers. 

***Silas rushed through a car which was nearly falling down the cliff. If he interacts with the trigger placed to the left of two ammo crates placed right after this...***

Silas: I found the device they used to blow the tracks, so I knew I was headed in the right direction.

***END OF ALTERNATE ROUTE***

***"My ears are still ringing from blowing up that bridge!" "What did you say? I can't hear a goddamn thing!"*** ***"Shit! That's Silas Greaves!" "What the hell!"***

Silas: Well I made my way off unscathed and came upon a few members of the gang and had no choice but to dispatch them. From there I had to negotiate an even more precarious route. But first I would need to get my ass out of there. I jumped from the frying pan into the fire as that train was clearly fixing to fall. I had found the gang but in order to find old Bob I needed to fight my way forward past whole a passel of desperadoes. Outside, inside, anyway I could I made my way towards my prey.

Molly: But what about the passengers?

Silas: It was mostly a freight train as I recall, there were no passengers aboard that day.

***Silas opened a door leading to a cliff.***

Silas: As I mentioned before I am not fond of heights, but I was too busy dodging bullets to worry about falling to my death. Odds were I was likely to die that day anyway, so I was determined to take down as many of those bastards as I could.

***Silas then crosses paths with a car with powder barrels and bad guys in it. He can move forward without blowing the car, if the player rather.***

Silas: I kept hoping the law would show up and give me a hand- ***As he mentioned before, he had no interest in joining the Pinkerton Circus, but much like when he was hunting down the Daltons, a little help was welcome.***

Dwight: You mean like that giant Pinkerton Posse that I read about? Did they come riding in, guns ablazing to help?

\textbf{***Joe Lefors, T. Jeff Carr, Tim Keliher, Elzy Lay, Kid Curry, Butch Cassidy, Sundance Kid: Grand Posse VS The Wild Bunch***} ***But actually no.***

Silas: Help? From the Pinkertons? No, son, I had to fight the Wild Bunch all by my lonesome. As usual. ***The Pinkertons despawn one by one.*** ***"Who the hell is that?" "He's out of his mind!" "Take cover! Retreat, retreat!" "He's killing everybody!"***

***Silas crosses the first car in the tunnel.***

Silas: My guess is those dime novels didn't portray this as it happened, did they? ***Well, you were the one who said to not believe everything you read in dime novels.***

***From this point on, you can either use the gatling gun or not. Your choice. Although using it at higher difficulties makes more sense.***

Silas: Only a few stragglers were left and I had to cut them down pronto if I was gonna stay on old Bob's trail. Once I silenced all those guns, I went searching for my nemesis, determined to finally have my justice. But the only survivor who welcomed me was George "Flatnose" Curry.

Jack: Who was he?

***The heartbeat plays as soon as the background music stops. Keep your ears open. An eagle cry will play if you go for a dishonored kill.***

Silas: The fastest gun in the gang. Right after Sundance, I mean. And Kid Curry. And maybe Elzy Lay. ***The fourth fastest gun in the gang, then. One way or another, he wasn't their best tool in the shed.*** On that very same day Butch Cassidy and the Sundance Kid ***And Roscoe "Bob" Bryant indeed*** decided to leave the Wild Bunch behind and decamp for South America. They ended up living down there for many years but I'm sure you already know all about that.

***They also died there, as we'll hear. Or sort of hear.***

\section*{1:30 To Hell}

\begin{quote}
    Parachute, CO (Colorado)

    June 7, 1904 -Five years after Wilcox train robbery
\end{quote}

Silas: I tried to find Bob Bryant but it was as if he had disappeared. Sometime later I heard the Wild Bunch was back together. Kid Curry escaped from jail and was now running the whole shebang. So I took to their trail. As I was still in pursuit of my brothers' killer and hoped he was back with them.

***"That Kid Curry was kind of crazy, hm?" "Don't let him hear you saying that."*** Anyways, I tracked those boys to a camp right outside Parachute, Colorado. Being outnumbered, I didn't bother with a warning shot. I just started taking those bastards down. ***Although some throwing knives would have made more sense.*** Old Bob wasn't among 'em and neither was Kid Curry. I could sense them close by, however, plotting something nasty. I just needed a clue as to their whereabouts.

***A plan is drawn on a rock in the camp.***

Silas: And I found one. A map with their bold plan clearly marked. This time they were fixing to blow up a train trestle. Property of the Union Pacific. ***No way it'd be another Wilcox incident, right?***

***Cuts to the next morning.***

Silas: The plan clearly indicated how they were fixing to undermine several of the weakest wooden supports. ***With strategically placed dynamite stacks.***

\begin{quote}
    The next morning, outside of Parachute
\end{quote}

Silas: Kid Curry was considered the wildest of the Wild Bunch. It was said he fathered 85 bastard children, though some say it was only five. Kid Curry had bragged to a whore how he was gonna rob a train heading to the U.S. mint in Denver. And that whore, Fat Sally, she told me. The bridge was rigged with dynamite, so I decided I best be careful confronting those bastards. ***Thankfully, a lot less dynamite than in Bannack. Although paying attention to where you shoot never did anyone no harm... If you know what I mean. Also, the disarmed dynamite rigs are added as dynamite ammo.***

Silas: A moment later I saw a ladder that somehow had escaped my attention. ***A lot of paths in the trestle escaped his attention, actually.***

***"Don't you blow us up now." "Don't worry, I know what I'm doing!"*** ***Once again, be careful if you choose the rifle as your weapon of choice. The shot could traverse through the bad guy and hit the dynamite. Outcome: Trestle go boom.***

Silas: But the Wild Bunch did not take kindly to my presence and attempted to blow my head off. It appeared the Kid had found a number of new recruits to bolster their ranks. Guess there's always desperate men willing to trade their lives for stolen treasure.

Dwight: What happened next?

Silas: Well having removed that first bundle of dynamite, I decided I might as well remove the other one. ***There were three other charges set along with the disarmed two ones.*** Once that was done, I figured I'd find my way from there.

***And there were more bad guys. As mentioned, no way it'd be another Wilcox incident, since the area was well guarded this time.***

Dwight: So, what happened then?

Silas: Had to remove more of that damn dynamite. ***Three down, two to go.***

Molly: It must have been terrifying trying to make your way across.

Silas: I was sweating it a bit, but then I noticed a foot bridge tied up on high. So I shot the rope.

***If Silas dies by falling while in the trestle...***

Silas: ***He says something about he should be careful or he could, well... die. Anyway, this situation is rare to happen as well given the player is not dumb enough.***

***END OF ALTERNATE ROUTE***

Molly: So that was all the dynamite?

Silas: Funny you should mention that, darling, as actually there was a fourth charge impeding my progress. Once I removed it, my path was pretty clear. ***Only one charge left.*** So I proceeded onward... and realized that that way just wasn't gonna work. I needed an alternate path forward. Luckily, I found a cave and as I made my way back to the bridge, I saw something that concerned me. It was a long burning fuse and it was moving fast as well. I had to catch it! ***"It's gonna blow!"*** The burning fuse was so damn quick! I had to run like the wind! I almost had it, but no! Thought I was gonna have a coronary when I lost sight of those sparks! My heart was pounding like a sledgehammer! I knew that failure meant BOOM! Then, finally, at the last moment... ***Silas extinguishes the fuse.*** Phew. Of course I was successful or I clearly wouldn't be talking to you folks here today. Naturally, I removed the last dynamite charge. ***Well it was a.. touching reunion*** But, by this time, I was thoroughly exhausted and dragging my ass as I was not a young man anymore.

***If Silas looks back after getting off the overpass, he gets a beautiful view of the level he just went through. Don't stray away from the story though...*** ***"Kill that id(inaudible)"***

Silas: Just when I thought things couldn't get worse, Kid Curry opened up on me with a goddamn gatling gun. It was hidden in this tunnel and pretty well shielded.

\textbf{***Kid Curry***}

Silas: Luckily, I had located some dynamite. ***Triple dynamite, triple damage.*** I still, however, had my work cut out for me.

***Silas gets a third done with Curry.***

Kid Curry: Goddamn! I need some help here! Come on boys! Take this sumbitch out! Flank this cocksucker! Move it, boys! Beef that bastard!

Silas: Eventually, I brought that tunnel down and that's when I met Kid Curry himself. He had decided to stop pussyfooting around and deal with me personally.

***Make sure to charge at least 90\% of speed and focus or Silas will be easily pwned.***

Silas: As fast as he was, I was just a bit faster. And as he lay wounded, I demanded to know the whereabouts of Roscoe "Bob" Bryant. He shouted at me: "Is that what this is about? Bob went with Butch and Sundance to South America. You ain't never finding him!" ***And the coward tries to hit Silas one last time.*** Those were his last words.

***At this point, Silas was pretty convinced his chances of ever finding Roscoe "Bob" Bryant had dropped to close to zero. Until...***

\section*{Death Rides A Steel Stallion}

Ben: So Bob Bryant got away?

Silas: I knew I'd never find him in South America.

Dwight: What about the other killer? ***Good question, Dwight.***

Steve: Yeah, you kind of glossed over that one.

Silas: Well, I found Jim not long after my showdown with Ringo. At the time, he was riding with the James-Younger Gang. Did I neglect to mention that?

Dwight: Jesse James?! The greatest outlaw who ever lived?!

Steve: Jesse and his kin rode with Quantrill when he raided Lawrence, Kansas, and killed near two hundred people, boy.

Ben: Uh, nothing great about that.

Steve: And from there, him and his brother went on to rob banks and trains from Kansas to Missouri!

Silas: Which is why there was such a rich bounty on their heads: Forty grand for the both of 'em, dead or alive. That's one well of a pay day. I confronted them as they were robbing a train. ***Bob Ollinger's shotgun plays in the background. Looks like BGM recycling is common too.*** Bullets were flying at me from every which way. But I knew I'd have to fight my way forward if I was gonna find this Jim.

Steve: Now wait a second, how'd they stop this train in the first place?

Silas: The James boys were experts at this. ***Indeed they were.***

\textbf{***Legend was... he could stop a train... by staring it down: Jesse James***}

Silas: They hopped a freight train, heaving heard... there was a biiig payroll in the express safe. So I hopped the same train.

\begin{quote}
    On the train ride from Winston, MO (Montana)
    
    Nearly 30 years ago ***After John Wesley Hardin's arrest***
\end{quote}

Silas: The James-Younger gang was decimated after that little fiasco they had in Northfield, Minnesota. So Jesse needed more men and took on the killer I was after along with a host of others. I was hoping to find my man and put a bullet in his head. Climbing around that train, I must have swallowed a hundred damn bugs before I reached t-

Dwight: The James-Younger gang pulled the first train robbery west of the Mississippi. ***Thanks, Dwight, for spoiling Silas' lies.***

Silas: Sounds like you hold them in high regard.

Dwight: Everyone knows they were the most famous outlaw gang ever.

Jack: And you took them on all by your lonesome... again? I'm finding this all a little hard to swallow, friend. ***Don't worry about Jack, he's just being loyal to a friend...***

Silas: Well, maybe you need to wash it down with some whiskey. By the way, did I mention that that train was flying down those tracks like a bat out of hell?

***Silas didn’t mind Jack calling him a liar, since he knew first-hand what happened. And Dwight just couldn't hold his fascination for these stories...***

Silas: Anyway... Excuse me, Ben, but where would I find the gentlemen's facilities? Suddenly, I have an urgent need to drain my one-eyed snake. Well, I've had more than a few drinks and, uh, I've been sitting here for quite a spell.

Ben: He-he-he-he, right through there, let me show you.

***First car copy***

Jack: I've never heard so much malarkey in my life.

Steve: Uh, you think he's bullshitting us?

Dwight: You don't think he's Silas Greaves? ***There's a Silas Greaves?***

Jack: I think he's just some old drunk looking for some free liquor.

***Second car copy***

Dwight: I don't know, Jack. I think I believe him. You don't think he met Jesse James? ***Sorry I have to ruin the legend for you, Eisenhower-boy, but he didn't meet Jesse James.***

Jack: Boy, you gotta be kidding me. That story makes no sense at all. ***Molly: Jack...*** You gotta be two bricks short of a load to believe that old cock and bull story.

Dwight: I don't agree.

Jack: Jack, lay off the boy. ***Silas in your playthrough didn't rush to the next car, did he?***

***Third car copy -a nugget is somewhere nearby...***

Jack: You seriously think that tired old man went toe-to-toe with Jesse James?

***Shshsh...***

Silas: Well that's better. Did I mention that this Jim was married to the infamous Belle Starr? Of course I didn't learn that until later. Anyway, I made my way forward the best I could: around the sides, over the roof. At some point, some son of a bitch saw me and shouted out: "It's the damn Pinkertons!" ***"It's the damn Pinkertons!" -The gameplay does not let Silas lie alone.*** Now I never worked for that limey prizesucker but I guess they assumed I was one of his assassins. Those evil bastards firebombed Jesse's mother's house and killed his stepbrother. ***A year later, some dumbasses from this very same circus did worse to the Marstons.*** So no wonder each and every asshole on that train wanted me dead.

Jack: Everybody's always mistaken you for somebody else, aren't they? Why is that, I wonder?

Silas: Don't rightly know, Jack. I'm just telling you how I remember it.

Jack: I bet you are.

***After passing a section of piled planks, Silas can shoot the chains holding the log piles down into the enemies.*** ***"Shoot that stupid son of a bitch!"***

Silas: Right about then I was attacked by some asshole on a gatling gun.

Jack: Eh, seems like you ran into a lot of them. ***Why is that, I wonder?***

Silas: Assholes?

Jack: Gatling guns.

Silas: Guess I did. Now I don't remember how I took it out. It was either a bullet or dynamite. ***It probably was dynamite. A bullet to take him out is tough at higher difficulties.***

Jack: Where would you find dynamite?

Silas: Does it really matter, Jack? You're messing with the flow of the story here. ***Yep, it was a stern-wheeler.*** I was looking for Jim and shooting any son of a bitch stupid enough to get in my way. And that included Jesse James himself. ***He probably shot him without noticing.*** There sure were a lot of men determined to die that day. It was then that Jesse detached the express car from the rest of the damn train. I could see Jesse waiting for me, fixing to kill me so he could get away with all that money. ***Now Silas was provoking Jack.*** ***Fun fact: If the player is fast enough, Silas can walk through the fire caused by the detachment.***

Dwight: You had a showdown with Jesse James?

Jack: Of course he didn't. Everybody knows that Jesse was killed by Bob Ford. ***Don't be stupid, Dwight. Those dime novels know nothing.***

Ben: Yeah. Jesse went out like John Wesley Hardin: A coward shot him in the back of the head. ***Okay, so maybe Silas is actually pulling our legs for some free booze.***

Silas: Guess it doesn't matter how far you run, does it, Ben? Your past always catches up with you. ***Or not entirely... I mean, why would Silas throw in a completely random sentence after such a sentence?*** Yeah, I didn't kill Jesse James. Just wounded him bad enough to convince him to hang up his guns. ***LIAR!***

Dwight: What about that Jim fella? What happened to him?

Silas: I figure he was up front, with a gun to the engineer's head. That bastard slipped away again. ***Lucky bastard, indeed*** I'll tell ya how I got him, but first I need to wet my whistle. ***No more booze for you, Silas Greaves... If that's your real name.***

\section*{Without Forgiveness}

Silas: After my showdown with Jesse, I continued to track his brother Frank and that sumbitch Jim. I followed those bastards into the high mountains as they were going to ground.

Jack: What mountains would that be?

\begin{quote}
    Ozark Mountains, hostile territory
    
    Some time after Winston train robbery
\end{quote}

Silas: Somewhere in the Ozarks, I believe. The perfect place to hide out from the authorities. ***Notice the pattern? That Grey Wolf story "Dances With Renegades" fits in perfectly here.*** In fact, before I could find them, some Indians who fled the res and were hiding out from the military found me first. They probably thought I was a Calvary scout and didn't want me telling the military where they were.

Jack: Injuns?

Silas: Eh, t-they could have been, eh, Cheyenne... but, there were all sorts of renegades roaming the landscape back then.

***A lot of them pin Silas down. And he deals with them with grace.***

Silas: Hey, how about another whiskey, Ben? Nothing better to soothe a troubled soul. ***He's provoking Ben now.***

***Silas reached a camp just like the one in the "Indian spell" he talked about earlier... Actually, it was that camp.***

Silas: Now where was I? Indians, right... I had more than my share of run-ins with the red man. Like that time- did I tell you about Grey Wolf?

Dwight: Yes, sir, you did.

Silas: Ah, of course I did. In fact, I can still remember that old medicine man's words to me.

Jack: Jesus Christ, we're back to that again?

Silas: You carry... great darkness in your heart. ***"...and if you do not release it..."*** It will claim your soul. You will come to this place again... And kill many more men... And the darkness will grow... ***Cuts back to the spell...*** ...Until it consumes everything you are.

Ben: So did you ever find 'em? ***That's the question I was talking about.***

***Cuts back to the Ozarks... enemies disappear.***

Silas: Who?

Ben: The man you were after?

Silas: Let me ask you something, Ben: You ever think about death?

Molly: Mr. Greaves, are you alright? ***Call him Silas, ma'am.***

Silas:
\begin{center}
    """
    
    Oh, Death. O-Oh, Death... Won't you spare me over 'til another year?
    
    What is this that I can't see? With ice cold hands... takin' hold of me.
    
    Well, I am death... none can excel... I'll open the door... to Heaven or Hell.
    
    Oh, Death... someone would pray... would you wait to call me... another day?
    
    ***A rain embraces the Ozarks. A thunder detaches some rocks on a cliff. The rocks roll down the hill.***
    
    No land. No wealth. No silver, no gold... Nothing satisfies me... but your soul.
    
    Oh, Death. O-Oh, Death... Won't you spare me over... for another year?
    
    Oh, Death. O-Oh, Death... Won't you spare me over... for another year?
    
    """
\end{center}

***The fact that many players who played this game skipped this awesome singing by John Cygan is why pop culture is so toxic these days. But does that really matter?***

Ben: So are you gonna answer the question?

Silas: What question is that?

Ben: Jim Reed -did you ever find him? ***Silas used persuasion! It's very effective, since Ben gave away he knew the surname of that assmole Jim!***

Silas: Reed... was indeed that son of a bitch's surname. That's right, Ben. A despicable character. I remember him laughing like a hyena that cold morning they lynched me and my brothers. ***Prepares to cut to the next sequence.*** He was intent on avoiding my vengeance, but nothing was gonna stop me. Nothing. ***Jim deserved to die more than the other two...***

\textbf{***Frank James***}

Silas: I finally did track those outlaws down. They had long rifles with scopes and were well positioned to pick off any poor soul who came anywhere close. ***Actually, it was just one... and he only appeared if Sense of Death was triggered, which makes the health bar above the screen pointless.*** I'm guessing Frank James believed I was responsible for the demise of his brother Jesse. I couldn't really disagree with the man as I thought Jesse was dead than as well. He backed off as I closed in on him, but he was still intent on killing me. And when I closed in on him again, he backed off again, looking for a better angle on me. Well... I can't fault Frank for wanting his revenge as I was there for the same damn reason myself. At this point, I'm guessing you think Silas Greaves is a worse murderer than Jim Reed ever was. ***So he admits he's not Silas Greaves? Or is this a fourth-wall break?***

Dwight: No, sir.-

Silas: A man who spent half his life killing somebody's brothers, fathers, sons.

Dwight: I think you were just looking for justice, sir.

Silas: Is that what I was looking for, Dwight? ***Is that what you call it?*** Is that what it was? Justice?

***A big rock detaches from the edge of the cliff.***

Dwight: Isn't that why you were hunting the James Gang?

Silas: The James Gang... Right. I finally found Frank holed up in his mountain cabin and he was determined to have me dead. ***At this rate, Silas already noticed Dwight was the only one who wanted to listen to his stories.***

***Triple dynamite, triple damage. And you better be quick if you don't want to deal with more shotgunners.***

Frank James: End that son of a bitch! Take him out! He's just one man! Put him down! I want that bastard dead!

***Silas quickly gets done dynamiting that shack.***

Frank James: NOOOOOO!

Silas: And that old shack, well it went tumbling right off that cliff.

Steve: With Frank James still in it?

Silas: Yes sir.

Dwight: But Frank James is still alive, living in Missouri, showing folks around the family farm for 25 cents a tour.

Silas: I didn't say he died in the fall, now did I?

***Frank James climbs back up the cliff and sits in a near rock.***

Frank James: I'm done with this damnable outlaw life! Kill me, don't kill me, do what you will! At this point, I just don't give a shit!

Silas: I explained to Frank that I had nothing against him personally and that I was looking for someone else.

Frank James: You want Reed? Have at him. I never did like that bastard! I am done here!

Silas: We parted in peace as Frank pointed out the path to my prey before making his way back down the hill. ***Silas' shots can't hit Frank.***

Ben: So, what happened with Reed? ***Ironic how Ben wants to know so badly about what happened to Jim.***

Silas: Well I finally found the last of the gang hiding in a nearby cave. First I had to dispatch the lookouts. As I was determined not to let that murderer escape my revenge again. But rather than wander in willy-nilly, I decided it would be better to smoke that sumbitch out: "Hey Reed!", I shouted, "No wonder you're so ornery! Can't be easy being married to Belle Starr! While you're off providing for the family, she's spreading her legs for every Tom, Dick and Cole Younger! Not an attractive woman exactly but... very friendly! At least she was to me!"

Jim Reed: Son of a bitch!

Silas: It was then that the last bunch of bandits jumped out of hiding. ***For some reason, some bad guys have black skin models. Don't ask me why.*** Eventually, it was just me and Reed. ***Reed plays unfair, but you know what to do.*** I had waited a long time to face him down so I could repay him for what he did to my brothers. ***Another line with a rare chance of being randomly skipped by mysterious glitches. Which, by coincidence, have become common in video games over the past decade.*** And repay him I did. ***May God have mercy on his soul.***

***Call Of Juarez: Gunslinger brilliantly made up for the commercial and critical failure of Call Of Juarez: The Cartel, a present-day take on the franchise which should have never happened. But greed... is something you don't fight. Because you can't. Because it's organized as well. For one person who boycotts, ten other people provide sponsorship. And that's why the world is so fucked up right now.***

\section*{The Good, The Bad And The Dead}

Silas: Well, ehh, I don't know about you boys but I'm pretty beat.

Dwight: Well, it's too damn bad you never found that Bob character. It seems a shame he never had to pay.

Silas: Well, funny thing about that: I did have one more chance at him. Six months ago, I heard that Butch and Sundance were back in the states and had gathered up some of their old gang. ***From who? Jack?*** I tracked them down, hoping that Roscoe "Bob" Bryant had returned with them.

Jack: So you're saying they didn't die down in Bolivia?

Silas: That's what I'm saying.

***ENOUGH IS ENOUGH!***

\begin{quote}
    Wind River Mountains, Wyoming 1910
    
    Barely six months ago
\end{quote}

Silas: 40 years I had waited to get my hands on the last of my brothers' killers. Not even an army of demons could have stopped me now.

***It was damp and foggy. Pinetrees everywhere. It was probably afternoon. The bad guys came to Silas in hundreds.***

Silas: Both Johnny Ringo and Jim Reed fell fairly quickly. But the last one... Roscoe "Bob" Bryant, that son of a bitch had managed to escape my vengeance time and time again. I couldn't even be certain I'd recognize him after all those years. By now, he had to be close to seventy.

Ben: For all you know he could have been dead. ***Ben long noticed as well Silas already recognized he was Bob.***

Silas: That thought had indeed crossed my mind. As did others. For instance, did my thirst for vengeance turn me into something worse than the man I was after? By this point in my storied career I had killed more men than Bob Bryant ever had. I was furious as hell at that bastard for making me into who I am. A man with no family, no friends. No purpose except shooting Bob Bryant dead. Nothing... could stop me from taking his life. I'd been after that killer forever. From the time I rode with Billy the Kid. But that chapter of my story you already know.

Jack: Chapter of that fairy tale, you mean.

Silas: Suddenly it was 1910 and there I was: An old man roaming a ghost town dead almost two decades. ***A wooden plank falls from a barn.*** The town was falling apart, just like me. Even though the ghosts of my dead brothers were begging me to end what I had started so long ago. ***How come we don't get to learn the name of Silas' brothers?***

Molly: Mr. Greaves, are you alright? Would you like some water? ***Goddamnit, woman, don't you see he would?***

Silas: The Wild Bunch knew I was there. They were after a treasure they'd hidden before they fled, buried in the grave of a dead amigo. ***Missing that last period in the subtitles.*** Some folks think that town was haunted, so they figured there wouldn't be many people poking around.

***Once Silas enters the next shack, there's no turning back. But it has an upper floor in which the bad guys can't hit him.***

Silas: I intended to fill that grave with Bob Bryant's corpse. But like I said, the bandits knew I was onto them. They lured me in and hit me with everything they had. ***Alright, that does it: This man isn't Silas Greaves. Asshole ain't nothing but a dime novel fairy tale.***

Steve: But you obviously prevailed, since you're sitting here telling us the tale.

Silas: Actually, in that moment, I did not prevail.

Jack: So I suppose we're talking to a ghost! ***Indeed we are, Jack.***

Silas: Funny you should put it like that, Jack. ***"Back off, Grandpa!" A big explosion goes down and the screen fades.*** Because when I woke up...

Jack: Eh, from the dead?

Silas: There was silence all around me. I could swear to God I saw Billy then.

Steve: Billy who?

Silas: Billy the Kid... William Bonney. He was shooting at me from a rooftop. Here, there. Even over there! 

Jack: So I am right. You are teched in the head. ***Indeed you are.***

Molly: Mr. Greaves, perhaps we should switch you to coffee? ***And make him even more teched? Are you nuts?***

Jack: You see that old Indian again too? ***You mean, Grey Wolf?***

Silas: No, but I did see Billy's killer: Patrick Floyd Garrett. He came at me, guns ablazing! But I knew that old warhorse had died two years before. I wondered if maybe I was dead too and confronting the ghosts of my past. ***Wondered?*** Perhaps all my sins were coming back to haunt me and- and drag me down to perdition. I saw Henry Plummer throw dynamite at me. In the gates of the cemetery I saw John Wesley Hardin, just like I remembered him. Robert Ollinger appeared with his terrible double-barreled shotgun. But no ghost army was stopping me!

Steve: Eh, my father-in-law got hit with a falling branch. He spent the rest of his life talking to dogs.

Silas: Newman Haynes Clanton, William Brocius, John Peters Ringo: They all wanted me dead. The Dalton Brothers: Robert and Gratton. Guardians of the garden of the dead. George Curry and Harvey Logan, alias Kid Curry, both thirsty for vengeance from the great beyond. Jesse Woodson James and Jim Reed, each one deader than the next. I thought I would go crazy!

Jack: Thought?

Silas: Finally I saw Harry Alonzo Longabaugh.

Steve: The Sundance Kid?

Silas: Like a General leading his legion of the dead. 

Steve: He told us before you've seen him alive! Silas: He was alive. ***These two lines don't appear in subtitles.***

Silas: Then I heard a voice calling to me from afar. It was Robert LeRoy Parker a.k.a. Butch Cassidy, coming at me from out of the fog.

Butch Cassidy: Thanks for taking care of that bastard.

\textbf{***Butch Cassidy, Sundance Kid, Silas Greaves: The Good, The Bad And The Dead***} ***Apparently, Silas Greaves' model actually has eyes -harmed from a lifetime of bounty hunting, of course: <https://youtu.be/RmfQ-jHGT60?t=10026>***

Silas: But the Kid wasn't quite deceased. Not yet. ***The Sundance Kid, that is. Not Billy the Kid.***

Sundance Kid: It takes more than one little bullet to kill the likes of me, "partner".

Silas: Those two looked like they hadn't seen each other for quite a while. Clearly they were no longer amigos.

Butch Cassidy: Spit, I was hoping I wouldn't have to kill you.

Sundance Kid: You won't have to, Butch. I'm killing you first.

Silas: I asked them about Bob Bryant... but they were too busy with their own heated conversation.

Butch Cassidy: Let me get this spit straight: You want my money and the love of my life?

Sundance Kid: You frittered it all away Butch! ***Once again, misplaced placeholders: Subtitles say "You it frittered all".*** Etta's mine. And so is that damn money!

Silas: I didn't want to shoot anybody until I had an answer to my question, but those boys didn't give me much of a choice.

***Keep the rotating circle in the opponent's head and your hand close to your gun. When the rotating circle stops, switch targets. Follow the script and nothing to worry.***

Silas: Butch Cassidy and the Sundance Kid died there in that cemetery not six months ago. ***Looks like Silas has mistaken the two last ghosts with Butch and Sundance.***

\section*{Was "The Authentic Story Of Silas Greaves, Bounty Hunter" True?}

Jack: Butch Cassidy and the Sundance Kid were killed by the Bolivian Army, everybody knows that!

Silas: That's the legend, but it ain't the truth. ***The weight of a bounty-hunting life is too heavy to drop on a coward who simply collected all the 54 Nuggets of Truth.***

Ben: So you never found Bob? ***And Ben, indeed, was absolutely sure he'd escape Silas again.***

Jack: There is no "Bob". This old sumbitch ain't even Silas Greaves. ***As mentioned, Jack was just being loyal to a friend. Isn't that what you call it, Ben?***

Dwight: Sir, is that true? Have you been pulling our legs this whole time? ***And poor Eisenhower-boy, who once believed dime novels, now would listen to an asshole.***

Silas: Not the whole time.

Jack: Old man, I think you've worn out your welcome here.

Silas: Maybe you're right, Jack. Maybe it's time to pay. ***I wonder if that Spanish Coin Silas pulled right after looked like a hundred years old to Jack... if it did, he probably went like "Suit yourself then, fishhead".*** You see Ben, or should I say "Bob", your past always catches up with you.

***A cup cracks into the ground out of surprise.***

Ben: I-I-I was a different man back then, crazy, drinking, I... I've changed my ways, I swear to you. If I could turn back the clock, I-

Silas: But you can't, Bob. ***Nobody can.***

Ben: Why'd you toy with me like that? ***Why'd he toy with US like that?*** Telling those tales, knowing all along... ***What makes you think he knew all along?*** Why not just lay your cards on the table?

***Silas arrived in Abilene with little to no reasons for avenging Bryant. Such a thing at that rate was pretty useless since both of them have fallen from grace. But shall you insist, I'll just tell you what happens because the revenge route is not worth taking: Silas will say "I won't have it said I left you with nothing, 'Bob'", but will leave a bandoleer at the table instead of the Spanish Coin. The saloon gets into despair as Bob sees no other choice but defending himself. The duel against Bob is the only one in the game with disabled HUD regardless of difficulty. In shock, Dwight stays beside Steve, which reveals he shouldn't be exposed to such an atrocity since he's leaving for West Point next morning. Also, Molly says she's calling the sheriff and that's it. If you want to get the other ending, you'll have to play through the entire "The Good, The Bad And The Dead" mission again.***

Silas: Wanted to suss you out, Bob. See what kind of man you turned out to be. ***Maybe that "Don't I know you, sir?" gave away to Silas he was the man he was after... Maybe he just followed the clues and put the pieces of the jigsaw together.*** Maybe prod you into drawing on me. See, all those years on your trail turned me into a killer. Can't even remember who I was before you tried to murder me. ***{Clears throat} But he murdered your brothers, I mean, he was riding with the men who murdered your brothers.*** You, on the other hand, walked that very same path in exactly the opposite direction. ***He made the retirement of Frank James sound like shit.***

Ben: What do you mean by that?

Silas: You think your life is worth sparing, Bob? ***Silas thought it was, but in the end Bob was a dead man anyway.***

Ben: {Grunts in despair}

***Silas looks at Dwight.***

Silas: Boy, what's your name again?

Dwight: It's Eisenhower, sir. Dwight Eisenhower.

Silas: What do you plan to do with your life, Dwight Eisenhower?

Dwight: Eh, tomorrow I'll be leaving for West Point, sir.

Silas: So you wanna be a soldier? Well you do it right, son. Don't tear down the world out of anger and spite like I did. You build it up. You do something decent with your life. You hear me?

Dwight: Sir, yes sir.

***Silas leaves the Spanish Coin on the balcony.***

Silas: I won't have it said I left you with nothing, "Bob".

***And so, Silas Greaves leaves the Bull's Head, off to a well-earned retirement.***

Call Of Juarez: Gunslinger is an action game developed by Techland and published by Ubisoft which was released in 2013.

***

Note: After some investigation listening to \href{https://www.youtube.com/playlist?list=PL6NsvPsFxD9bRzacDEDLdyhoWxGPFiW2T}{the awesome soundtrack of this game} and trying out \href{https://www.gamepressure.com/download.asp?ID=74332}{the free camera of a dev menu mod}, it came to my attention the stories of Silas Greaves are told in three rooms (game dev designation for levels): Borderlands, Wilderness and Train (where "Death Rides A Steel Stallion" takes part). These rooms are rearranged according to the upcoming chapter. This dev menu mod has an invoke menu which provides quick access to the checkpoints of the chapters which take part in a certain room. I can only suggest that, following we already know the game has been rushed due to parts of the dialogue which may be skipped if Silas rushes and a couple subtitle typos, this game had a massive potential to be open-world, given Dead Island was already a hit back then.

***

Need for more Silas Greaves?:

\href{https://store.steampowered.com/app/3020/?curator_clanid=4777282&utm_source=SteamDB}{Call of Juarez}

\href{https://store.steampowered.com/app/21980/?curator_clanid=4777282&utm_source=SteamDB}{Call of Juarez: Bound in Blood}

\end{document}
