\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{indentfirst} % Always indent first paragraphs
\usepackage{hyperref} % Allows using \href function
\usepackage[normalem]{ulem} % To use \sout function to strikethrough
% https://www.tablesgenerator.com/ generates LaTeX tables

\begin{document}

\begin{table}[]
    \begin{tabular}{cc}
        \textbf{In Black Ops Cold War} & \textbf{In Black Ops}      \\
        Nowhere Left to Run            & Operation 40               \\
        CIA Safehouse E9               & U.S.D.D.                   \\
        Fracture Jaw                   & S.O.G.                     \\
        East Berlin Briefing           & -                          \\
        Brick in the Wall              & The Defector               \\
        Redlight, Greenlight           & Project Nova               \\
        Echoes of a Cold War           & WMD                        \\
        Lubyanka Briefing              & -                          \\
        Desperate Measures             & Vorkuta                    \\
        Cuba Briefing                  & -                          \\
        End of the Line                & Payback                    \\
        Interrogation                  & -                          \\
        Break on Through               & Rebirth                    \\
        Identity Crisis                & Revelations                \\
        The Final Countdown            & Redemption                 \\
        Ashes to Ashes                 & Victor Charlie, Crash Site \\
        Operation Chaos                & Numbers                    \\
        Operation Red Circus           & Executive Order           
    \end{tabular}
\end{table}

Full transcripts are available at Call of Duty wiki.

\rule{8cm}{0.4pt}

\begin{quote}
    “We must realize that no arsenal or no weapon in the arsenals of the world is so formidable as the will and moral courage of free men and women. It is a weapon our adversaries in today's world do not have. Let that be understood by those who practice terrorism and prey upon their neighbors.” Ronald Reagan
\end{quote}

\begin{quote}
    NOWHERE LEFT TO RUN
    
    Alex Mason - \sout{CIA Operative}
    
    Amsterdam, \sout{The Netherlands}
    
    \sout{January 12} 1981
\end{quote}

With the world at the verge of a full-scale war, our CO Emerson Black pulled two names linked to a hostage situation in Tehran. First up was Qasim Javadi. Plenty of men to cover a single high-value target. It was a capture mission at first, but maybe the cold blood of my teammates risked the op. Intel's keeping an eye out anyway.

Next up, we had Arash Kadivar. He and his men were ready to leave the Trabzon Airfield in Turkey and we were ready to crash their party... if it wasn't them crashing their own party first. After bringing their plane to a spectacular halt, Arash spitted out the name we wanted:

“His plan is already underway! You won't be able to stop him this time. \href{https://callofduty.fandom.com/wiki/Perseus_(Cold_War)}{Perseus}.”

\begin{quote}
    CIA Safehouse E9 "Die Landebahn"
    
    \sout{[player first name]} "Bell" \sout{[player last name]},
    
    \sout{52.5200 N, 13.4050 E,} West Berlin
    
    \sout{February 23,} 1981
\end{quote}

First day in the regiment is always the hardest one: Pretty new faces, but none of them thinks you can be trusted. However, following the executing approval of the President of the United States, there was no way our huntdown to the Perseus spy ring could go wrong.

\begin{quote}
    Fracture Jaw
    
    \sout{[player first name]} "Bell" \sout{[player last name]},
    
    Camp Haskins, Vietnam
    
    January 26, 1968
\end{quote}

1968. Khe Sanh. The U.S. was convinced the Reds were supporting the locals in the hopes of getting their hands on high-quality merchandise. \href{https://callofduty.fandom.com/wiki/S.O.G./Transcript?so=search}{Some say a defector died back then with intel on the whereabouts of the gear}. My new CO, Russell Alder, grants that I was on Da Nang, also assisting the units in looking for intel linking the locals to the Reds. Part of me doesn't remember such, though, despite he kept claiming:

“We had a job to do”.

\begin{quote}
    East Berlin, Germany
    
    \sout{[player first name]} "Bell" \sout{[player last name]},
    
    East Berlin, \sout{German Democratic republic}
    
    \sout{February 24,} 1981
\end{quote}

After I spitted out everything I knew, they decrypted a certain \href{https://callofduty.fandom.com/wiki/Anton_Volkov}{Anton Volkov}, a Russian Arms Dealer possibly connected to Perseus. It was kill or capture: Getting him out of the scene would blast a big damage in the ring, but bringing him in would come in handy long-term. A certain \href{https://callofduty.fandom.com/wiki/Franz_Kraus}{Franz Kraus} was our way to get to him. Somehow he knew we were tailing him. And he was ready.

Once again, the only thing stopping us was our cold blood while dealing with the Stasi and a certain \href{https://callofduty.fandom.com/wiki/Lukas_Richter}{Lukas Richter}, long time partners with Greta. But it turned out he was working for Volkov now.

\begin{quote}
    \underline{REDLIGHT, GREENLIGHT}
    
    \sout{[player first name]} "Bell" \sout{[player last name]}
    
    \sout{The Zakarpatska Oblast,} Ukraine, \sout{USSR}
    
    \sout{February 27,} 1981
\end{quote}

Once we were done with Volkov, it was time for the bigger fish: A nuke smuggled through East Berlin by the spy ring. They were holding it in a bunker. That place was a complete training ground for the Reds: Complete with an arcade, mannequins and even a Burger Town.

We reached a computer center with the recordings we needed. It turns out I wasn't the only one to not be trusted by the CIA: Operation Greenlight was a series of American nukes scattered throughout Europe in case of World War III. And, right now, Perseus had one of them.

\begin{quote}
    ECHOES OF A COLD WAR
    
    \sout{Alex} Mason \sout{- CIA Operative}
    
    Mount Yamantau, \sout{Ural Mountains, USSR}
    
    \sout{March 3,} 1981
\end{quote}

There was no time to whine. As my teammates still couldn't believe what they saw, they were on their way back to \href{https://callofduty.fandom.com/wiki/WMD_(mission)/Transcript?so=search}{Yamantau} in order to find names of suspects of smuggling that nuke. Possibly or not related to Perseus.

\begin{quote}
    DESPERATE MEASURES
    
    Dmitri Belikov - \sout{Head of KGB Security}
    
    \sout{KGB Headquarters}, Moscow
    
    \sout{March 9}, 1981
\end{quote}

The mainframe they pulled out of Yamantau was a huge gold mine, except for one thing: Plenty of missing names. It was time to bring out the big guns again: Me and Adler would have to infiltrate the Lubyanka building, in the heart of the Motherland, to find those remaining names. \href{https://callofduty.fandom.com/wiki/Dimitri_Belikov}{Belikov} had a few ideas on how to get us a keycard, but most of those ideas were risky: Gorbachev consented General Charkov should keep the only key to the bunker, since the building was on lockdown because of an impostor which was in. He could poison him, frame him or have him killed by an inmate, or he could take the less risky route by making a copy of the key.

\begin{quote}
    DESPERATE MEASURES
    
    "Bell", \sout{Assault Team}
    
    \sout{KGB HQ Basement,} Moscow
    
    \sout{March 9,} 1981
\end{quote}

Once all done, me and Adler would come in: Keycard in hand, even a checkpoint checkup wouldn't stop us -it's a good thing Belikov was good at timing. Once we started pulling out the names, the whole building would be on alert. Causing a ruckus wasn't the most subtle approach, but it was the best choice at the time.

\begin{quote}
    END OF THE LINE
    
    "Bell"\sout{, CIA/MI6/Ex-KGB/Classified}
    
    \sout{30 Miles South of Havana,} Cuba
    
    \sout{March 13,} 1981
\end{quote}

It was time to kick the hornet's nest: \href{https://callofduty.fandom.com/wiki/Theodore_Hastings}{Theodore Hastings} was the name we were after. He was assigned to take the smuggled nuke to Cuba. It was a bit of a slog, but we shot all our way through. Only to find out a man who looked like \href{https://callofduty.fandom.com/wiki/Perseus_(Cold_War)?so=search}{Kraus} was cleaning house. All because we just learned Perseus didn't have his hands in a single Operation Greenlight nuke: He had ALL of them. And he was ready to set them off and blame it all in the U.S.

\begin{quote}
    BREAK ON THROUGH
    
    "Bell"\sout{, CIA/MI6/Ex-KGB/Classified}
    
    Central Highlands, South Vietnam
    
    July 16th, 1968
\end{quote}

With no other options for the team left, Adler took the risk of unburying something I had: A memory of an operation I took part back in 'Nam. Which, as usual, I didn't remember jack. In that operation, I may have taken different approaches and used different weapons, but I reached a bunker. In this bunker, the whole Perseus spy ring was there, discussing the approach to take out the U.S. in their tracks. And I was part of it.

Until they cleared house on January 81. It was when they arrived and rescued me. They implemented those false memories on me to protect me from the Reds. And whenever they needed to recall them, they just need a name and a motto:
“We had a job to do... Bell”.

Now I had to give them an answer which could change the world forever:
“Where is Perseus”?

\begin{quote}
    \underline{Ashes to Ashes}
    
    \sout{[First Name]} "Bell" \sout{[Last Name], [Affiliation]}
    
    Duga-2 \sout{Radar Array, Khabarovsk Krai, USSR}
    
    \sout{March 15,} 1981
\end{quote}

I could have told them he was in Duga. All the spy ring members were there, but not the nukes. I would have driven them straight into a trap: Outgunned and outnumbered, they would succumb quickly to our forces. Maybe I'd even give Adler the honor of one last cigar. After that, they would comment on how my expertise was fundamental for the success of the Soviet operation.

\begin{quote}
    \underline{THE FINAL COUNTDOWN}
    
    "Bell"\sout{, MI6}
    
    \sout{The} Solovetsky \sout{Islands, USSR}
    
    \sout{March 15,} 1981
\end{quote}

Instead, I told them he was in Solovetsky. None of the spy ring members were there, but the nukes were going to go off from there. Stopping these nukes sent an even bigger message to Perseus than taking out the ring. President Reagan was relieved and Commander Black was satisfied with the outcome of the American operation. As for me, my fate remains unresolved to this day.

\begin{center}
    Bell was not the Impostor.
    
    1 Impostor remains.
\end{center}

\end{document}
